MCC Models

### 2019-04-03 papers/full_paper/manuscript.Rmd
first draft full paper

Studying how multiple types of social information are balanced contributes to a comprehensive and ecologically valid model of word learning. In the current study, participants inferred the referent by integrating non-linguistic cues (speakers turning and looking to one table) with assumptions about speaker informativeness and common ground information. However, in addition to social information, children can use semantic and syntactic features of the utterances as cues to the meaning of the words embedded therein [e.g. @clark1973s; @abend2017bootstrapping; @gleitman1990structural]. The everyday learning environment is complex and combines non-linguistic, linguistic as well as pragmatic cues. Across development, children learn to recruit these different sources of information and integrate them. Our studies show how computational models of language use and comprehension can be used as powerful tools to explicate and test hypothesis about how integration proceeds.

>>>>

Studying how multiple types of social information are balanced contributes to a comprehensive and ecologically valid model of word learning. In the current study, participants inferred the referent by integrating non-linguistic cues (speakers turning and looking to one table) with assumptions about speaker informativeness and common ground information. However, the real learning environment is much richer than the what we captured in our experimental design. In addition to multiple layers of social information, children can rely on semantic and syntactic features of the utterances as cues to the meaning of the words embedded therein [@clark1973s; @abend2017bootstrapping; @gleitman1990structural]. Across development, children learn to recruit these different sources of information and integrate them. Our studies show how computational models of language use and comprehension can be used as powerful tools to explicate and test hypothesis about how integration proceeds.
